Titeln på avhandlingens språk

### 2022-08-31 publications/2021ImpactDelayedResponse/body.tex
plos

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
% \usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}
\usepackage{tabularx}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% % Use the PLoS provided BiBTeX style
% \bibliographystyle{plos2015}

% % Remove brackets from numbering in List of References
% \makeatletter
% \renewcommand{\@biblabel}[1]{\quad#1.}
% \makeatother

% BibLatex and PLOS One hacks
% \usepackage[citestyle=numeric,
%             backend=bibtex,
%             bibstyle=authoryear,
%             sorting=none,
%             sortcites,
%             firstinits,
%             terseinits,
%             maxbibnames=6,
%             dashed=false]{biblatex}
% \bibliography{bibliography}
\usepackage{cite}

\usepackage[colorlinks]{hyperref}

% Name list format
% \renewcommand*{\labelnamepunct}{\addspace}
% \renewcommand*{\finalnamedelim}{%
%   \ifbibliography{\addcomma\space}{\addspace\&\space}}
% \renewcommand*{\revsdnamepunct}{}
% \DeclareNameAlias{sortname}{last-first}

% No quotes or italics in titles
% \DeclareFieldFormat{title}{#1}
% \DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,
%                     thesis,unpublished]{title}{#1}
% \DeclareFieldFormat{journaltitle}{#1}
% \DeclareFieldFormat{issuetitle}{#1}
% \DeclareFieldFormat{maintitle}{#1}

% \renewbibmacro*{in:}{%
%   \ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}

% Remove page prefixes
% \DeclareFieldFormat{pages}{#1}

% Only print journal volume
% \renewbibmacro*{volume+number+eid}{%
%   \setunit*{\addspace}%
%   \printfield{volume}}

% Use colon for volume-pages delimiter
% \renewcommand*{\bibpagespunct}{%
%   \ifentrytype{article}{\addcolon\space}{\addcomma\space}}

% Add labelnumbers to bibliography
% \DeclareFieldFormat{labelnumberwidth}{#1\adddot}
% \defbibenvironment{bibliography}
%   {\list
%      {\printtext[labelnumberwidth]{%
%       \printfield{prefixnumber}%
%       \printfield{labelnumber}}}
%      {\setlength{\labelwidth}{\labelnumberwidth}%
%       \setlength{\leftmargin}{\labelwidth}%
%       \setlength{\labelsep}{\biblabelsep}%
%       \addtolength{\leftmargin}{\labelsep}%
%       \setlength{\itemsep}{\bibitemsep}%
%       \setlength{\parsep}{\bibparsep}}%
%       \renewcommand*{\makelabel}[1]{\hss##1}}
%   {\endlist}
%   {\item}

% Omit authoryear disambiguation
% \AtEveryBibitem{\clearfield{extrayear}}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

% other packages
\usepackage[capitalize, nameinlink]{cleveref}
\usepackage[inline]{enumitem}
\usepackage[binary-units, range-units=single, range-phrase=~to~, list-units=single]{siunitx}
\sisetup{
    detect-all,
    detect-inline-family=math,
    detect-inline-weight=math,
    detect-display-math=true,
    list-final-separator = {, and }
}
\usepackage{subcaption}
\usepackage{amsthm}
\usepackage{thmtools}

\declaretheoremstyle[
notefont=\bfseries, notebraces={}{},
bodyfont=\normalfont,
headformat=\NAME~\NUMBER~---~\NOTE%
]{nopar}
\declaretheorem[style=nopar]{definition}

\usepackage[export]{adjustbox}
\usepackage{multirow}
\usepackage{booktabs}

\usepackage{pgf-umlsd}
\usepackage{tikz}
\usepackage{tikzpeople}
\usetikzlibrary{shapes,arrows.meta,positioning,automata,matrix,shapes.symbols,trees}
\usepackage{tikz-qtree}
\usepackage[]{todonotes}
\reversemarginpar  % todonotes on left

\newenvironment{acks}{
  \section*{Acknowledgements}
}{}

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Impact of delayed response on Wearable Cognitive Assistance} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Manuel~{Olguín~Muñoz}\textsuperscript{1, *},
Roberta~Klatzky\textsuperscript{2, 3},
Junjue~Wang\textsuperscript{4},
Padmanabhan~Pillai\textsuperscript{5},
Mahadev~Satyanarayanan\textsuperscript{4},
James~Gross\textsuperscript{1}
\\
\bigskip
\begin{tabularx}{\textwidth}{lX}
  \textbf{1} & Division of Information~Science and Engineering, School of Electrical~Engineering and Computer~Science, KTH Royal Institute~of~Technology, Stockholm, Sweden\\
  \textbf{2} & Department of Psychology, Carnegie~Mellon~University, Pittsburgh, PA, USA\\
  \textbf{3} & Human-Computer Interaction Institute, Carnegie~Mellon~University, Pittsburgh, PA, USA\\
  \textbf{4} & School of Computer Science, Carnegie~Mellon~University, Pittsburgh, PA, USA\\
  \textbf{5} & Intel Labs, Pittsburgh, PA, USA\\
\end{tabularx}
\bigskip

\begin{tabularx}{\textwidth}{lX}
  % \Yinyang & These authors contributed equally to this work.\\
  % \ddag & Senior author.\\
  * & Corresponding author: \href{mailto:molguin@kth.se}{\texttt{molguin@kth.se}}\\
\end{tabularx}

\end{flushleft}
% Please keep the abstract below 300 words

@@

\linenumbers%
\section{Introduction}

@@

\nolinenumbers%

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
%

% \bibliographystyle{plos2015}
% \bibliography{bibliography}
\begin{thebibliography}{10}

  \bibitem{Ha:TowardsWearableCogAssist}
  Ha K, Chen Z, Hu W, Richter W, Pillai P, Satyanarayanan M.
  \newblock Towards Wearable Cognitive Assistance.
  \newblock In: Proceedings of the 12th Annual International Conference on Mobile
    Systems, Applications, and Services. MobiSys '14. New York, NY, USA: ACM;
    2014. p. 68--81.
  \newblock Available from: \url{http://doi.acm.org/10.1145/2594368.2594383}.

  \bibitem{Chen:EarlyImplementation}
  Chen Z, Jiang L, Hu W, Ha K, Amos B, Pillai P, et~al.
  \newblock Early Implementation Experience with Wearable Cognitive Assistance
    Applications.
  \newblock In: Proceedings of the 2015 Workshop on Wearable Systems and
    Applications. WearSys '15. New York, NY, USA: ACM; 2015. p. 33--38.
  \newblock Available from: \url{http://doi.acm.org/10.1145/2753509.2753517}.

  \bibitem{IKEAAssistant}
  {IKEA assistant}; 2020.
  \newblock Available from: \url{https://www.youtube.com/watch?v=vMzTGgQHjpo}.

  \bibitem{satya2019augmenting}
  {Satyanarayanan} M, {Davies} N.
  \newblock {Augmenting Cognition Through Edge Computing}.
  \newblock Computer. 2019;52(7):37--46.
  \newblock doi:{10.1109/MC.2019.2911878}.

  \bibitem{Chen:AnEmpiricalStudyOfLatency}
  Chen Z, Hu W, Wang J, Zhao S, Amos B, Wu G, et~al.
  \newblock An Empirical Study of Latency in an Emerging Class of Edge Computing
    Applications for Wearable Cognitive Assistance.
  \newblock In: Proceedings of the Second ACM/IEEE Symposium on Edge Computing.
    SEC '17. New York, NY, USA: ACM; 2017. p. 14:1--14:14.
  \newblock Available from: \url{http://doi.acm.org/10.1145/3132211.3134458}.

  \bibitem{funk2015caworkplace}
  {Funk} M, {Schmidt} A.
  \newblock Cognitive Assistance in the Workplace.
  \newblock IEEE Pervasive Computing. 2015;14(3):53--55.

  \bibitem{gorecky2011cognito}
  Gorecky D, Worgan SF, Meixner G.
  \newblock {COGNITO: A Cognitive Assistance and Training System for Manual Tasks
    in Industry}.
  \newblock In: Proceedings of the 29th Annual European Conference on Cognitive
    Ergonomics. ECCE '11. New York, NY, USA: Association for Computing Machinery;
    2011. p. 53--6.
  \newblock Available from: \url{https://doi.org/10.1145/2074712.2074723}.

  \bibitem{PingPongAssistant}
  {Ping Pong assistant}; 2020.
  \newblock Available from: \url{https://www.youtube.com/watch?v=_lp32sowyUA}.

  \bibitem{dabrowsky:2011:40years}
  Dabrowski J, Munson EV.
  \newblock {40 years of Searching for the Best Computer System Response Time}.
  \newblock Interact Comput. 2011;23(5):555–564.
  \newblock doi:{10.1016/j.intcom.2011.05.008}.

  \bibitem{haapalainen2010psycho}
  Haapalainen E, Kim S, Forlizzi JF, Dey AK.
  \newblock Psycho-physiological measures for assessing cognitive load.
  \newblock In: Proceedings of the 12th ACM international conference on
    Ubiquitous computing; 2010. p. 301--310.

  \bibitem{kumar2016measurement}
  Kumar N, Kumar J.
  \newblock Measurement of cognitive load in {HCI} systems using {EEG} power
    spectrum: an experimental study.
  \newblock Procedia Computer Science. 2016;84:70--78.

  \bibitem{john1999:bfi}
  John OP, Srivastava S, et~al.
  \newblock The Big Five trait taxonomy: History, measurement, and theoretical
    perspectives.
  \newblock Handbook of personality: Theory and research. 1999;2(1999):102--138.

  \bibitem{hirsh2008delay}
  Hirsh JB, Morisano D, Peterson JB.
  \newblock Delay discounting: Interactions between personality and cognitive
    ability.
  \newblock Journal of research in personality. 2008;42(6):1646--1650.

  \bibitem{witmer1998:itq}
  Witmer BG, Singer MJ.
  \newblock Measuring presence in virtual environments: A presence questionnaire.
  \newblock Presence. 1998;7(3):225--240.

  \bibitem{olguin:2018}
  {Olguín Muñoz} M, {Wang} J, {Satyanarayanan} M, {Gross} J.
  \newblock Demo: Scaling on the Edge --- A Benchmarking Suite for
    Human-in-the-Loop Applicationss.
  \newblock In: 2018 IEEE/ACM Symposium on Edge Computing (SEC); 2018. p.
    323--325.

  \bibitem{olguin:2019}
  {Olguín Muñoz} M, Wang J, Satyanarayanan M, Gross J.
  \newblock EdgeDroid: An Experimental Approach to Benchmarking Human-in-the-Loop
    Applications.
  \newblock In: Proceedings of the 20th International Workshop on Mobile
    Computing Systems and Applications. HotMobile '19. New York, NY, USA:
    Association for Computing Machinery; 2019. p. 93–98.
  \newblock Available from: \url{https://doi.org/10.1145/3301293.3302353}.

  \bibitem{neves1981knowledge}
  Neves DM, Anderson JR.
  \newblock Knowledge Compilation: Mechanisms for the.
  \newblock Cognitive skills and their acquisition. 1981;6:57.

  \bibitem{zakay1995attentional}
  Zakay D, Block RA.
  \newblock An attentional-gate model of prospective time estimation.
  \newblock Time and the dynamic control of behavior. 1995; p. 167--178.

  \bibitem{zakay1996role}
  Zakay D, Block RA.
  \newblock The role of attention in time estimation processes.
  \newblock In: Advances in psychology. vol. 115. Elsevier; 1996. p. 143--164.

  \bibitem{bruno2016multiple}
  Bruno A, Cicchini GM.
  \newblock Multiple channels of visual time perception.
  \newblock Current opinion in behavioral sciences. 2016;8:131--139.

  \bibitem{wiener2011multiple}
  Wiener M, Matell MS, Coslett H.
  \newblock Multiple mechanisms for temporal processing.
  \newblock Frontiers in integrative neuroscience. 2011;5:31.

  \bibitem{heron2012duration}
  Heron J, Aaen-Stockdale C, Hotchkiss J, Roach NW, McGraw PV, Whitaker D.
  \newblock Duration channels mediate human time perception.
  \newblock Proceedings of the Royal Society B: Biological Sciences.
    2012;279(1729):690--698.

  \bibitem{matthews2011stimulus}
  Matthews WJ.
  \newblock Stimulus repetition and the perception of time: The effects of prior
    exposure on temporal discrimination, judgment, and production.
  \newblock PLoS one. 2011;6(5).

  \bibitem{droit2011emotion}
  Droit-Volet S, Fayolle SL, Gil S.
  \newblock Emotion and time perception: effects of film-induced mood.
  \newblock Frontiers in integrative neuroscience. 2011;5:33.

  \bibitem{Loewenstein1992anomaliesintertemporalchoice}
  Loewenstein G, Prelec D.
  \newblock {Anomalies in Intertemporal Choice: Evidence and an Interpretation*}.
  \newblock The Quarterly Journal of Economics. 1992;107(2):573--597.
  \newblock doi:{10.2307/2118482}.

  \bibitem{nielsen1994usability}
  Nielsen J.
  \newblock Usability engineering.
  \newblock Morgan Kaufmann; 1994.

  \bibitem{shneiderman2016designing}
  Shneiderman B, Plaisant C, Cohen M, Jacobs S, Elmqvist N, Diakopoulos N.
  \newblock Designing the user interface: strategies for effective human-computer
    interaction.
  \newblock Pearson; 2016.

  \bibitem{seow2008designing}
  Seow SC.
  \newblock Designing and engineering time: The psychology of time perception in
    software.
  \newblock Addison-Wesley Professional; 2008.

  \bibitem{jeon2015degree}
  Jeon H, Friederici AD.
  \newblock Degree of automaticity and the prefrontal cortex.
  \newblock Trends in cognitive sciences. 2015;19(5):244--250.

  \bibitem{puttemans2005changes}
  Puttemans V, Wenderoth N, Swinnen SP.
  \newblock Changes in brain activation during the acquisition of a
    multifrequency bimanual coordination task: from the cognitive stage to
    advanced levels of automaticity.
  \newblock Journal of Neuroscience. 2005;25(17):4270--4278.

  \bibitem{lewis2003distinct}
  Lewis PA, Miall RC.
  \newblock Distinct systems for automatic and cognitively controlled time
    measurement: evidence from neuroimaging.
  \newblock Current opinion in neurobiology. 2003;13(2):250--255.

  \bibitem{koch2009neural}
  Koch G, Oliveri M, Caltagirone C.
  \newblock Neural networks engaged in milliseconds and seconds time processing:
    evidence from transcranial magnetic stimulation and patients with cortical or
    subcortical dysfunction.
  \newblock Philosophical Transactions of the Royal Society B: Biological
    Sciences. 2009;364(1525):1907--1918.

  \bibitem{lee2019limiting}
  Lee TG, Acuña DE, Kording KP, Grafton ST.
  \newblock Limiting motor skill knowledge via incidental training protects
    against choking under pressure.
  \newblock Psychonomic bulletin \& review. 2019;26(1):279--290.

  \bibitem{baumeister74tice}
  Baumeister RE, Bratslavsky E, Muraven M.
  \newblock Tice (1998). Ego Depletion: Is the Active Self a Limited Resource.
  \newblock Journal of personality and social psychology;74(5):1252.

  \bibitem{lin2020strong}
  Lin H, Saunders B, Friese M, Evans NJ, Inzlicht M.
  \newblock Strong effort manipulations reduce response caution: A preregistered
    reinvention of the ego-depletion paradigm.
  \newblock Psychological science. 2020; p. 0956797620904990.

  \bibitem{pijpers2003anxiety}
  Pijpers JRR, Oudejans RRD, Holsheimer F, Bakker FC.
  \newblock Anxiety--performance relationships in climbing: a process-oriented
    approach.
  \newblock Psychology of sport and exercise. 2003;4(3):283--304.

  \bibitem{khawadi2015:usinggsrtrust}
  Khawaji A, Zhou J, Chen F, Marcus N.
  \newblock {Using Galvanic Skin Response (GSR) to Measure Trust and Cognitive
    Load in the Text-Chat Environment}.
  \newblock In: Proceedings of the 33rd Annual ACM Conference Extended Abstracts
    on Human Factors in Computing Systems. CHI EA ’15. New York, NY, USA:
    Association for Computing Machinery; 2015. p. 1989–1994.
  \newblock Available from:
    \url{https://doi-org.focus.lib.kth.se/10.1145/2702613.2732766}.

  \bibitem{kuikkaniemi2010:biofeedback}
  Kuikkaniemi K, Laitinen T, Turpeinen M, Saari T, Kosunen I, Ravaja N.
  \newblock The Influence of Implicit and Explicit Biofeedback in First-Person
    Shooter Games.
  \newblock In: Proceedings of the SIGCHI Conference on Human Factors in
    Computing Systems. CHI ’10. New York, NY, USA: Association for Computing
    Machinery; 2010. p. 859–868.
  \newblock Available from:
    \url{https://doi-org.focus.lib.kth.se/10.1145/1753326.1753453}.

  \bibitem{solovey2014:classifyingdriverworkload}
  Solovey ET, Zec M, {Garcia Perez} EA, Reimer B, Mehler B.
  \newblock Classifying Driver Workload Using Physiological and Driving
    Performance Data: Two Field Studies.
  \newblock In: Proceedings of the SIGCHI Conference on Human Factors in
    Computing Systems. CHI ’14. New York, NY, USA: Association for Computing
    Machinery; 2014. p. 4057–4066.
  \newblock Available from:
    \url{https://doi-org.focus.lib.kth.se/10.1145/2556288.2557068}.

  \bibitem{peterson1907psycho}
  Peterson F, Jung CG.
  \newblock Psycho-physical investigations with the galvanometer and pneumograph
    in normal and insane individuals.
  \newblock Brain. 1907;30:153--218.

  \bibitem{Healey2005}
  Healey JA, Picard RW.
  \newblock Detecting Stress During Real-World Driving Tasks Using Physiological
    Sensors.
  \newblock {IEEE} Transactions on Intelligent Transportation Systems.
    2005;6(2):156--166.
  \newblock doi:{10.1109/tits.2005.848368}.

  \bibitem{Son2010}
  Son J, Reimer B, Mehler B, Pohlmeyer AE, Godfrey KM, Orszulak J, et~al.
  \newblock Age and cross-cultural comparison of drivers' cognitive workload and
    performance in simulated urban driving.
  \newblock International Journal of Automotive Technology. 2010;11(4):533--539.
  \newblock doi:{10.1007/s12239-010-0065-6}.

  \bibitem{Antonenko2010}
  Antonenko P, Paas F, Grabner R, van Gog T.
  \newblock Using Electroencephalography to Measure Cognitive Load.
  \newblock Educational Psychology Review. 2010;22(4):425--438.
  \newblock doi:{10.1007/s10648-010-9130-y}.

  \bibitem{Grimes2008}
  Grimes D, Tan DS, Hudson SE, Shenoy P, Rao RPN.
  \newblock Feasibility and pragmatics of classifying working memory load with an
    electroencephalograph.
  \newblock In: Proceeding of the twenty-sixth annual {CHI} conference on Human
    factors in computing systems - {CHI} {\textquotesingle}08. {ACM} Press;
    2008.Available from: \url{https://doi.org/10.1145/1357054.1357187}.

  \bibitem{empatica:e4}
  {Empatica E4}; 2020.
  \newblock Available from: \url{https://www.empatica.com/research/e4/}.

  \bibitem{ragot2017emotion}
  Ragot M, Martin N, Em S, Pallamin N, Diverrez JM.
  \newblock Emotion recognition using physiological signals: laboratory vs.
    wearable sensors.
  \newblock In: International Conference on Applied Human Factors and Ergonomics.
    Springer; 2017. p. 15--22.

  \bibitem{mccarthy2016validation}
  McCarthy C, Pradhan N, Redpath C, Adler A.
  \newblock Validation of the {Empatica E4} wristband.
  \newblock In: 2016 IEEE EMBS International Student Conference (ISC). IEEE;
    2016. p. 1--4.

  \bibitem{openbci:headbandkit}
  {OpenBCI EEG Headband Kit}; 2020.
  \newblock Available from:
    \url{https://shop.openbci.com/products/openbci-eeg-headband-kit?variant=8120393760782}.

  \bibitem{eeg1020system:1961}
  The Ten Twenty Electrode System: International Federation of Societies for
    Electroencephalography and Clinical Neurophysiology.
  \newblock American Journal of EEG Technology. 1961;1(1):13--19.
  \newblock doi:{10.1080/00029238.1961.11080571}.

  \bibitem{agarwal2017eeg}
  Agarwal S, Rani A, Singh V, Mittal AP.
  \newblock {EEG signal enhancement using cascaded S-Golay filter}.
  \newblock Biomedical Signal Processing and Control. 2017;36:194--204.

  \bibitem{FUJIKOSHI1993ANOVA}
  Fujikoshi Y.
  \newblock {Two-way ANOVA models with unbalanced data}.
  \newblock Discrete Mathematics. 1993;116(1):315 -- 334.
  \newblock doi:{https://doi.org/10.1016/0012-365X(93)90410-U}.

  \bibitem{quesnel2018you}
  Quesnel D, Riecke BE.
  \newblock Are you awed yet? How virtual reality gives us awe and goose bumps.
  \newblock Frontiers in psychology. 2018;9:2158.

  \end{thebibliography}
\end{document}

>>>>

@@

\section{Introduction}

@@
